Cross-scale integration of knowledge for predicting species ranges: a metamodeling framework

### 2014-09-19 tex/proposal_letter.tex
Mostly final changes

We present a novel application of hierarchical Bayesian methods to integrating the predictions of multiple models into a single metamodel of a species distribution.
There is great interest in modeling species ranges, resulting in a great diversity of modeling approaches.
However, in general, individual approaches include only a small subset of the total available information about a species. 
For example, a broad-scale correlative model might use climate variables to predict presence or absence, but ignore what is known about smaller-scale processes such as the effect of local climate on growth, fecundity, and dispersal rates.
Furthermore, individual models often produce distinct predictions for the same species, with no simple way to reconcile these predictions.
Our framework is highly flexible and can integrate information from sub-models operating a multiple spatial and temporal scales.
The resulting meta-model framework produces probabilistic estimates of species presence that includes uncertainty from data sources as well as all sub-models.
 These predictions reflect all of the information used as input for the original sub-models.
We illustrate the metamodeling approach using two examples, and demonstrate that the framework can substantially reduce uncertainty when projecting beyond the range of some of the original data sources.
We conclude by discussing the application of our method and its accessibility to conservation biologists and land managers.
We believe that our manuscript represents an important step toward a more holistic approach for forecasting future species ranges.
Due to the importance of range shifts for both theoretical and applied ecology, the topic is of broad interest, and we hope you will find it of interest for the \emph{Ideas and Perspectives} section.

>>>>

We present a novel application of hierarchical Bayesian methods to integrating the predictions of multiple models into a single metamodel of a species distribution.
There is great interest in modeling species ranges, resulting in a great diversity of modeling approaches.
However, in general, individual approaches include only a small subset of the total available information about a species. 
For example, a broad-scale correlative model might use climate variables to predict presence or absence, but ignore what is known about smaller-scale processes such as the effect of local climate on growth, fecundity, and dispersal rates.
Furthermore, individual models often produce distinct predictions for the same species, with no simple way to reconcile these predictions.
Our framework is highly flexible and can integrate information from sub-models operating a multiple spatial and temporal scales.
The resulting metamodel framework produces probabilistic estimates of species presence that includes uncertainty from data sources as well as all sub-models.
 These predictions reflect all of the information used as input for the original sub-models.
We illustrate the metamodeling approach using two examples, and demonstrate that the framework can substantially reduce uncertainty when projecting beyond the range of some of the original data sources.
We conclude by discussing the application of our method and its accessibility to conservation biologists and land managers.
We believe that our manuscript represents an important step toward a more holistic approach for forecasting future species ranges.
Due to the importance of range shifts for both theoretical and applied ecology, the topic is of broad interest, and we hope you will find it of interest for the \emph{Ideas and Perspectives} section.
